\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}      % For UTF-8 support
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{booktabs}            % For nicer tables
\usepackage{hyperref}            % For hyperlinks in the document
\usepackage{graphicx}            % For images
\usepackage{array}               % For extended table features
\usepackage{setspace}
\geometry{margin=1in}
\setstretch{1.15}
% \title{This is Main title \\ [0.2em]\large This is Subtitle}
\title{Used Car Characteristics \\ [0.2em]\large An Explanatory Data Analysis}
\author{D치vid Fodor \and Faisal Zayeem Ahmed \and M치ri칩 Pal치gyi}
\date{Submission date: TBD}

\begin{document}

\maketitle

\section*{Abstract}
A brief overview of the project, including problem statement, methodology, key findings, and conclusions.

\section{Introduction}
\textbf{Problem Statement:} Describe the problem.\\[1ex]
\textbf{Objectives:} List the objectives and tasks required to be completed.\\[1ex]
\textbf{Data:} Describe your dataset.\\[1ex]
\textbf{Background Information:} Provide context and challenges based on your understanding of the problem.

\section{Literature Review}
Summary of relevant research and related works in the field. This section does not need to be exhaustive; include background knowledge on how the problem has been addressed before and how you plan to solve it.

\section{Methodology}
\begin{itemize}
    \item \textbf{Data Collection, Description and Management:} Describe the steps involved in data collection or preprocessing, including EDA.
    \item \textbf{Analysis Techniques:} Describe your approach to solving the problem. You can include a model diagram to illustrate your method.
    \item \textbf{Tools and Software Used:} List the tools, frameworks, and software used for the project.
\end{itemize}

\section{Results}
Describe experiments and the evaluation protocol. Include tables, graphs, and charts as needed to present your findings and results.

\section{Discussion}
Interpret and analyze the results, and discuss possible future work and improvements.

\section{Conclusion}
Provide a summary of the project, key findings, and recommendations. (Approximately 200--350 words.)

\section{Bibliography}
Include relevant references such as websites, blogs, articles, research papers, etc.

\section{Self-Reflection}
Add a paragraph or half-page note reflecting on the project.

\end{document}